Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-22 analysis/quarto/paper.qmd
rewrite intro & positioning

---
title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
author:
  - name: Hauke Roggenkamp
    email: hauke.roggenkamp@unisg.ch
    affiliations:
        - id: HSU
          name: Helmut Schmidt University
          department: Department of Economics
          address:  Holstenhofweg 85
          city: Hamburg
          state: Germany
          postal-code: 22043
        - id: HSG
          name: University of St. Gallen
          department: Institute for Behavioral Science and Technology
          address: Torstrasse 25
          city: St. Gallen
          state: Switzerland
          postal-code: 9000
    # attributes:
    #     corresponding: true
    # note: This is the first author footnote.
abstract: |
  I revisit the dynamic public good game by Gächter et al. (2017) developed to study cooperation under dynamic interdependencies. Collecting data from both students and a general population sample, I not only reproduce some of the author's original observations but also test the game's generalizability. Appending a charitable dictator game, I find no correlations between behavior in the abstract game and the charitable context. This applies to students and the general population sample alike. Studying inexperiend general population samples raises methodological challenges with respect to fatigue and dropouts. This paper approaches them and provides simple solutions to run relieable interactive experiments online.

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future. Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals. This applies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].

Public good games---although often intended to inform climate policies (e.g. @MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period. Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods. A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game. Here, participants' actions in a given period affect their number of actions in subsequent periods. Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of their treatments to compare dynamics across samples.

@GKLS2020 find that standard public good games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation. Greater resemblance improves generalizability. Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one wonders whether it is better suited to inform public policy. To approach this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] and
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA). This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples. The article shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.

The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.

@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an inconvenient sample: one that is completely inexperienced sample that has not been exposed to interactive experiments before. This required me to design a robust (and thus, more complex) software to minimize attrition. In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment. This article reports on both topics: the robust design as well as the feasibility.

@@

Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research. Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between (a) and (b). Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide. More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see e.g. @SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).

@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the label _'pre-registration'_ can be obtained with minimal effort. In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible. Even more so, they may have adverse effects as the label _'pre-registered'_ becomes cheap (too) to acquire.

@@

In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]

@@

Considering the design, the only differences between such a _static_ game and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth she accumulated in the first period. A participant's endowment in the third period is the wealth she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public good game.

>>>>

---
title: Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation
author:
  - name: Hauke Roggenkamp
    email: hauke.roggenkamp@unisg.ch
    affiliations:
        - id: HSU
          name: Helmut Schmidt University
          department: Department of Economics
          address:  Holstenhofweg 85
          city: Hamburg
          state: Germany
          postal-code: 22043
        - id: HSG
          name: University of St. Gallen
          department: Institute for Behavioral Science and Technology
          address: Torstrasse 25
          city: St. Gallen
          state: Switzerland
          postal-code: 9000
    # attributes:
    #     corresponding: true
    # note: This is the first author footnote.
abstract: |
  I revisit the dynamic public good game by Gächter et al. (2017) developed to study cooperation under dynamic interdependencies. Collecting data from both a convenient (students) and an inconvenient (general population) sample, I not only reproduce some of the author's original observations but also test their novel game's generalizability. Appending a charitable dictator game, I find no correlations between behavior in the charitable context and the dynamic game. This applies to students and the general population sample alike. Because the study of inexperiend general population samples raises methodological challenges, such as fatigue and dropouts, this research approaches them. Doing so, I and provide simple solutions to run relieable interactive experiments online.

@@

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it requires more effort in the future compared to a path that includes immediate action. Aiming at certain goals, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform climate policies (e.g. @MilinskiEtAl2006, @TavoniEtAl2011, @Hauser2014, @BrickEtAl2015, @GomezEtAl2018, @CalzolariEtAl2018, @CookEtAl2019)---miss these temporal interdependencies simply because participants have the same set of actions in each period. Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods. To see the lack of realism, consider carbon dioxide emissions, where the current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018]. Playing with fresh endowments in each period is as if one could just undo carbon dioxide emissions at no cost.

A game designed by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017 hereafter, GMTV] as well as Stefan Große (2011, unpublished) shows that it is fairly simple to remedy that flaw. They incorporated interdependencies into a _dynamic_ public good game by defining endowments as the income of previous periods. To put it differently, participants' actions in a given period affect their number of actions in subsequent periods: the more (less) they earn now, the more (less) they can contribute in the next period. Importantly, this modification qualitatively yields the same rational predictions as the static game (i.e. free-riding and the under-provision of the public good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on interdependencies^[One exemption are @Moser2019, who built on GMTV's design to investigate leadership.], I reproduced one of GMTV's treatments to compare dynamics across (in)experienced samples to investigate its generalizability.
@GKLS2020 find that static public good games do not generalize well to real-world climate action. They also find that generalizability depends on structural resemblance of the public goods game with the context of climate change mitigation: Greater resemblance improves generalizability. Because GMTV's dynamic setting has a more realistic property—namely, interdependencies—one would expect it to be better suited to inform public policy. To test this intuition, I not only ran the experiment with different samples but also
<!--, that is, with participants who make their decisions in an environment which is more natural than the lab.-->
observed the participants' behavior in voluntary climate actions (VCA).^[The VCA is a (charitable) dictator games where each participant is a dictator dividing her budget between herself and some organization linked to the reduction of CO2 emissions. @EckelGrossman1996 were the first to implement a charitable dictator game observing contributions of 30% of the endowments. Like @GKLS2020, @CarpenterEtAl2008 report that students make lower contributions to charity than community members.] This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples. This research shows that the dynamic setting _does not_ add any advances with respect to generalizability of results.

@AGM2018 conducted static public good games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see also @GoodmanPaolacci2017  @AmirEtAl2012] by focusing on an _inconvenient_ sample (i.e. one that is completely inexperienced sample that has not been exposed to interactive experiments before) playing a computationally more complex game. This required me to design a robust (and thus, more complex) software to minimize attrition. I collected paradata to assess the desired fluency and feasibility of the experiment. This research reports on the robust design that made the dynamic game feasible.

@@

Now, 20 years later, we accustom ourselves with mechanisms designed to unravel the fuzzy back-and-forth between exploratory and confirmatory research. Prominently, pre-registrations were established to tie the researchers' hands when doing confirmatory research--reducing observable discrepancies between Daryl Bem's above-mentioned (a) and (b). Today, researchers can not only choose where to pre-register but also decide about the level of detail they provide. More severely, nothing stops researchers from pre-registering multiple hypotheses opposing each other (see e.g. @SimmonsEtAl2021 and @PhamEtAl2021 for a discussion).

@WaldronAllen2022 report a wide variety of depth of pre-registrations in the field of Neuropsychopharmacology and document that the _'pre-registered'_ label can be obtained with minimal effort. In absence of transparency and scrutiny pre-registrations run into danger to miss the target of making science more credible. Even more so, they may have adverse effects as the _'pre-registered'_ label becomes cheap (too) to acquire.

@@

In fact, the experiment reported in this article qualifies for the _'pre-registered'_ label at a first glance:
The analysis was pre-registered in the American Economic Association's RCT Registry [@preregistration]. Further, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]

@@

Considering the design, the only differences between such a _static_ game (with partner matching) and GMTV's design are _dynamics_: Instead of receiving fresh endowments every period, participants receive one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth she accumulated in the first period. A participant's endowment in the third period is the wealth she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public good game.

### 2023-05-22 analysis/quarto/paper.tex
rewrite intro & positioning

\begin{abstract}
I revisit the dynamic public good game by Gächter et al.~(2017)
developed to study cooperation under dynamic interdependencies.
Collecting data from both students and a general population sample, I
not only reproduce some of the author's original observations but also
test the game's generalizability. Appending a charitable dictator game,
I find no correlations between behavior in the abstract game and the
charitable context. This applies to students and the general population
sample alike. Studying inexperiend general population samples raises
methodological challenges with respect to fatigue and dropouts. This
paper approaches them and provides simple solutions to run relieable
interactive experiments online.

@@

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it makes it more
difficult in the future. Hence, today's actions (or the omission
thereof) not only affect intermediate outcomes but also the number of
paths one can choose to reach certain goals. This applies especially to
carbon dioxide emissions where its current stock will last for well over
a millennium \citep{Inman2008, CalzolariEtAl2018}.

Public good games---although often intended to inform climate policies
(e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
interdependencies simply because participants have the same set of
actions in each period. Accordingly, participants' actions in a given
period do not affect their number of actions in subsequent periods. A
game designed by Gächter, Mengel, Tsakas \& Vostroknutov
\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
unpublished) incorporated interdependencies into a \emph{dynamic} public
good game. Here, participants' actions in a given period affect their
number of actions in subsequent periods. Because there is surprisingly
little experimental research on these interdependencies\footnote{One
  exemption are \citet{Moser2019}, who built on GMTV's design to
  investigate leadership.}, I reproduced one of their treatments to
compare dynamics across samples.

\citet{GKLS2020} find that standard public good games do not generalize
well to real-world climate action. They also find that generalizability
depends on structural resemblance of the public goods game with the
context of climate change mitigation. Greater resemblance improves
generalizability. Because GMTV's dynamic setting has a more realistic
property---namely, interdependencies---one wonders whether it is better
suited to inform public policy. To approach this question, I ran the
experiment with different samples\footnote{GMTV ran their experiments
  with students in Nottingham, England.} and observed the participants'
behavior in voluntary climate actions (VCA). This yielded a setting
similar to \citet{GKLS2020}'s which allows me to analyze how behavior in
the abstract game translates into real-world action across samples. The
article shows that the dynamic setting \emph{does not} add any advances
with respect to generalizability of results.

The VCA is a (charitable) dictator games where each participant is a
dictator dividing her budget between herself and some organization
linked to the reduction of CO2 emissions. \citet{EckelGrossman1996} were
the first to implement a charitable dictator game observing
contributions of 30\% of the endowments. Like \citet{GKLS2020},
\citet{CarpenterEtAl2008} report that students make lower contributions
to charity than community members.

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][ \citet{AmirEtAl2012}]{GoodmanPaolacci2017}
by focusing on an inconvenient sample: one that is completely
inexperienced sample that has not been exposed to interactive
experiments before. This required me to design a robust (and thus, more
complex) software to minimize attrition. In exchange, the online setting
allowed me to also collect paradata to assess the fluency and
feasibility of the experiment. This article reports on both topics: the
robust design as well as the feasibility.

@@

Now, 20 years later, we accustom ourselves with mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations were established to tie the
researchers' hands when doing confirmatory research--reducing observable
discrepancies between (a) and (b). Today, researchers can not only
choose where to pre-register but also decide about the level of detail
they provide. More severely, nothing stops researchers from
pre-registering multiple hypotheses opposing each other (see e.g.
\citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a discussion).

\citet{WaldronAllen2022} report a wide variety of depth of
pre-registrations in the field of Neuropsychopharmacology and document
that the label \emph{`pre-registration'} can be obtained with minimal
effort. In absence of transparency and scrutiny pre-registrations run
into danger to miss the target of making science more credible. Even
more so, they may have adverse effects as the label
\emph{`pre-registered'} becomes cheap (too) to acquire.

@@

In fact, the experiment reported in this article qualifies for the label
\emph{`pre-registered'} at a first glance: Parts of the analyses were
pre-registered in the American Economic Association's RCT Registry
\citep{preregistration}. In addition, I pre-registered the exact
analyses I planned to run when I designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}

@@

Considering the design, the only differences between such a
\emph{static} game and GMTV's design are \emph{dynamics}: Instead of
receiving fresh endowments every period, participants receive one
endowment only at the beginning of the first period. A participant's
endowment in the second period is the wealth she accumulated in the
first period. A participant's endowment in the third period is the
wealth she accumulated in the first two periods. And so on. Hence, a
decision in one period has consequences on future endowments and,
ultimately, growth paths. For this reason, the game is described as a
\emph{dynamic} public good game.

>>>>

\begin{abstract}
I revisit the dynamic public good game by Gächter et al.~(2017)
developed to study cooperation under dynamic interdependencies.
Collecting data from both a convenient (students) and an inconvenient
(general population) sample, I not only reproduce some of the author's
original observations but also test their novel game's generalizability.
Appending a charitable dictator game, I find no correlations between
behavior in the charitable context and the dynamic game. This applies to
students and the general population sample alike. Because the study of
inexperiend general population samples raises methodological challenges,
such as fatigue and dropouts, this research approaches them. Doing so, I
and provide simple solutions to run relieable interactive experiments
online.

@@

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it requires more
effort in the future compared to a path that includes immediate action.
Aiming at certain goals, today's actions (or the omission thereof) not
only affect intermediate outcomes but also the number of paths one can
choose from that lead to that specific goal.

Public good (or public bad) games---although often intended to inform
climate policies (e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
interdependencies simply because participants have the same set of
actions in each period. Accordingly, participants' actions in a given
period do not affect their number of actions in subsequent periods. To
see the lack of realism, consider carbon dioxide emissions, where the
current stock will last for well over a millennium
\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
each period is as if one could just undo carbon dioxide emissions at no
cost.

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
shows that it is fairly simple to remedy that flaw. They incorporated
interdependencies into a \emph{dynamic} public good game by defining
endowments as the income of previous periods. To put it differently,
participants' actions in a given period affect their number of actions
in subsequent periods: the more (less) they earn now, the more (less)
they can contribute in the next period. Importantly, this modification
qualitatively yields the same rational predictions as the static game
(i.e.~free-riding and the under-provision of the public good). It is
thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on
interdependencies\footnote{One exemption are \citet{Moser2019}, who
  built on GMTV's design to investigate leadership.}, I reproduced one
of GMTV's treatments to compare dynamics across (in)experienced samples
to investigate its generalizability. \citet{GKLS2020} find that static
public good games do not generalize well to real-world climate action.
They also find that generalizability depends on structural resemblance
of the public goods game with the context of climate change mitigation:
Greater resemblance improves generalizability. Because GMTV's dynamic
setting has a more realistic property---namely, interdependencies---one
would expect it to be better suited to inform public policy. To test
this intuition, I not only ran the experiment with different samples but
also observed the participants' behavior in voluntary climate actions
(VCA).\footnote{The VCA is a (charitable) dictator games where each
  participant is a dictator dividing her budget between herself and some
  organization linked to the reduction of CO2 emissions.
  \citet{EckelGrossman1996} were the first to implement a charitable
  dictator game observing contributions of 30\% of the endowments. Like
  \citet{GKLS2020}, \citet{CarpenterEtAl2008} report that students make
  lower contributions to charity than community members.} This yielded a
setting similar to \citet{GKLS2020}'s which allows me to analyze how
behavior in the abstract game translates into real-world action across
samples. This research shows that the dynamic setting \emph{does not}
add any advances with respect to generalizability of results.

\citet{AGM2018} conducted static public good games in the lab and on
MTurk to draw lessons from online experimentation. This study extends
this literature \citep[see also][
\citet{AmirEtAl2012}]{GoodmanPaolacci2017} by focusing on an
\emph{inconvenient} sample (i.e.~one that is completely inexperienced
sample that has not been exposed to interactive experiments before)
playing a computationally more complex game. This required me to design
a robust (and thus, more complex) software to minimize attrition. I
collected paradata to assess the desired fluency and feasibility of the
experiment. This research reports on the robust design that made the
dynamic game feasible.

@@

Now, 20 years later, we accustom ourselves with mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations were established to tie the
researchers' hands when doing confirmatory research--reducing observable
discrepancies between Daryl Bem's above-mentioned (a) and (b). Today,
researchers can not only choose where to pre-register but also decide
about the level of detail they provide. More severely, nothing stops
researchers from pre-registering multiple hypotheses opposing each other
(see e.g. \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
discussion).

\citet{WaldronAllen2022} report a wide variety of depth of
pre-registrations in the field of Neuropsychopharmacology and document
that the \emph{`pre-registered'} label can be obtained with minimal
effort. In absence of transparency and scrutiny pre-registrations run
into danger to miss the target of making science more credible. Even
more so, they may have adverse effects as the \emph{`pre-registered'}
label becomes cheap (too) to acquire.

@@

In fact, the experiment reported in this article qualifies for the
\emph{`pre-registered'} label at a first glance: The analysis was
pre-registered in the American Economic Association's RCT Registry
\citep{preregistration}. Further, I pre-registered the exact analyses I
planned to run when I designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}

@@

Considering the design, the only differences between such a
\emph{static} game (with partner matching) and GMTV's design are
\emph{dynamics}: Instead of receiving fresh endowments every period,
participants receive one endowment only at the beginning of the first
period. A participant's endowment in the second period is the wealth she
accumulated in the first period. A participant's endowment in the third
period is the wealth she accumulated in the first two periods. And so
on. Hence, a decision in one period has consequences on future
endowments and, ultimately, growth paths. For this reason, the game is
described as a \emph{dynamic} public good game.
